# Data transformation

```{r, include = FALSE}
library(tidyverse)
library(lubridate)
```

The initial step in cleaning the data was to combine the 7 data frames each containing 50,000 observations into one data frame containing 300,000 observations.

```{r, message=FALSE, include=FALSE}
df <- full_join(df_2015, df_2016, by = c("Id", "AcceptedAnswerId", "CreationDate", "LastActivityDate", "Tags", "AnswerCount", "CommentCount", "ViewCount", "Title")) %>%
  full_join(df_2017, by = c("Id", "AcceptedAnswerId", "CreationDate", "LastActivityDate", "Tags", "AnswerCount", "CommentCount", "ViewCount", "Title")) %>%
  full_join(df_2018, by = c("Id", "AcceptedAnswerId", "CreationDate", "LastActivityDate", "Tags", "AnswerCount", "CommentCount", "ViewCount", "Title")) %>%
  full_join(df_2019, by = c("Id", "AcceptedAnswerId", "CreationDate", "LastActivityDate", "Tags", "AnswerCount", "CommentCount", "ViewCount", "Title")) %>%
  full_join(df_2020, by = c("Id", "AcceptedAnswerId", "CreationDate", "LastActivityDate", "Tags", "AnswerCount", "CommentCount", "ViewCount", "Title")) %>%
  full_join(df_2021, by = c("Id", "AcceptedAnswerId", "CreationDate", "LastActivityDate", "Tags", "AnswerCount", "CommentCount", "ViewCount", "Title"))
```

Now, there are three things that need to changed in our data before it can be used for this analysis;

-   The Tags need to be separated so that we can compare the usage of each tag individually
-   We need to create a new variable to indicate whether or not there was an accepted answer based off of whether or not we were supplied an AcceptedAnswerId which we will refer to as AcceptAnswer
-   Convert AcceptAnswer, Tags and Id into factors, and convert CreationDate and LastActivityDate into dates

```{r, include=FALSE}
df <- df %>% 
  separate_rows(Tags, sep = "<") %>%
  separate_rows(Tags, sep = ">") %>%
  na_if("") %>%
  drop_na(Tags)

df <- df %>%
  mutate(AcceptAnswer = ifelse(is.na(AcceptedAnswerId), 0, 1))

df <- df %>%
  mutate(Id = as.factor(Id)) %>%
  mutate(Tags = as.factor(Tags)) %>%
  mutate(AcceptAnswer = as.factor(AcceptAnswer)) %>%
  mutate(CreationDate = as.Date(CreationDate)) %>%
  mutate(LastActivityDate = as.Date(LastActivityDate))

```


For our purposes we can omit title since we already have the post Id as a source of identification and we can omit AcceptedAnswerId because we only need the frequency of accepted answers which we have identified in AcceptAnswer.

```{r, include=FALSE}
df <- df %>%
  dplyr::select(Id, CreationDate, LastActivityDate, Tags, AnswerCount, CommentCount, ViewCount, AcceptAnswer)

```
